% Conveyor belt
\addcontentsline{toc}{subsection}{conveyor}
\Huge\bfseries conveyor : \large Conveyor belt\par
\noindent\rule{ \textwidth }{2pt}\par
\vspace{ 0.5cm }
\mdseries\normalsize This is the conveyor belt device. \textbf{Start}ing a conveyor belt makes it move items at a rate of 30cm/s. \textbf{Stop}ping a conveyor belt stops it. \textbf{Read}ing a belt does nothing.

\pagebreak

% End effector
\addcontentsline{toc}{subsection}{endeffector}
\Huge\bfseries endeffector : \large End effector\par
\noindent\rule{ \textwidth }{2pt}\par
\vspace{ 0.5cm }
\mdseries\normalsize This is the device on the end of the robot arm. It can grab packages. \textbf{Start}ing an end effector makes it grab packages. \textbf{Stop}ping an end effector makes it release packages. \textbf{Read}ing an end effector does nothing.

\pagebreak

% Laser
\addcontentsline{toc}{subsection}{laser}
\Huge\bfseries laser : \large Laser sensor\par
\noindent\rule{ \textwidth }{2pt}\par
\vspace{ 0.5cm }
\mdseries\normalsize This device shoots a laser and returns 1 if the laser is obstructed. \textbf{Start}ing a laser does nothing. \textbf{Stop}ping a laser does nothing. \textbf{Read}ing a laser returns 1 if the laser is obstructed, 0 if the laser is unobstructed.

\pagebreak

% Bin
\addcontentsline{toc}{subsection}{Bin}
\Huge\bfseries bin : \large Bin\par
\noindent\rule{ \textwidth }{2pt}\par
\vspace{ 0.5cm }
\mdseries\normalsize Holds items. \textbf{Start}ing a bin does nothing. \textbf{Stop}ping a bin does nothing. \textbf{Read}ing a bin returns the amount of packages contained inside it.

\pagebreak

% Bin Mover
\addcontentsline{toc}{subsection}{Bin Mover}
\Huge\bfseries binmover : \large Bin Mover\par
\noindent\rule{ \textwidth }{2pt}\par
\vspace{ 0.5cm }
\mdseries\normalsize Moves bins around on a track. \textbf{Start}ing a bin mover makes it go. \textbf{Stop}ping a bin mover makes it stop. \textbf{Read}ing a bin mover returns 1 if it is moving, 0 if it is stopped.

\pagebreak